\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-05-06 sections/introduction.tex
Change: Update the Results for draft v2

 This wealth of information on the composition and functions of a community at different times and under different environmental conditions has the potential to help us understand how communities assemble and operate.
 A powerful tool for translating microbiome composition data into knowledge is the construction of possible inter-dependence networks across species.
 The importance of these networks of relationships is two fold: first, such networks can serve as maps that help identify hubs of keystone species \cite{Menon2018,Rottjers2018}, and rewiring of interactions that occur as a consequence of environmental perturbations or underlying host conditions \cite{Gilbert2016}; second, networks of interdependencies can serve as a key bridge towards building mechanistic models of microbial communities, greatly enhancing our capacity to understand and control them.
 For example, multiple studies have shown the importance of specific microbial interactions in the healthy microbiome \cite{Lloyd-Price2016} and others have shown how changes in these interactions can lead to dysbiosis \cite{Wang2017,Gilbert2016,Belizario2015}.
 In the context of terrestrial bio-geochemistry, co-occurrence networks have been proposed as a valuable approach towards reconstructing the processes leading to microbiome assembly \cite{Fierer2017}, and understanding the response of microbial communities to environmental perturbations \cite{Jiao2019}.

>>>>

 This wealth of information on the composition and functions of a community at different times and under different environmental conditions has the potential to help us understand how communities assemble and operate.
 A powerful tool for translating microbiome composition data into knowledge is the construction of possible inter-dependence networks across species.
 The importance of these networks of relationships is two-fold: first, such networks can serve as maps that help identify hubs of keystone species \cite{Menon2018,Rottjers2018}, and rewiring of interactions that occur as a consequence of environmental perturbations or underlying host conditions \cite{Gilbert2016}; second, networks of interdependencies can serve as a key bridge towards building mechanistic models of microbial communities, greatly enhancing our capacity to understand and control them.
 For example, multiple studies have shown the importance of specific microbial interactions in the healthy microbiome \cite{Lloyd-Price2016} and others have shown how changes in these interactions can lead to dysbiosis \cite{Wang2017,Gilbert2016,Belizario2015}.
 In the context of terrestrial bio-geochemistry, co-occurrence networks have been proposed as a valuable approach towards reconstructing the processes leading to microbiome assembly \cite{Fierer2017}, and understanding the response of microbial communities to environmental perturbations \cite{Jiao2019}.
